Path Model Temperature Comparisons

### 2016-10-31 d-sep_test.Rmd
Add newline.

### Assess Independence Claims
The first independence claim is that `Date` is independent of `Latitude` after controlling for `DD`. So, I need to obtain the *precise* null probability for this claim. Choosing the correct modeling procedure requires identifying the appropriate distribution of the dependent variable, in this case `Date`. Using some helper fucntions and the `pairs()` function in the base `graphics` package I can look at the correlations and distributions simultaneously.
```{r helper functions for scatterplot matrix, echo=FALSE}
# These were copied from the help pages of the `pairs` function with minor alterations

>>>>

### Assess Independence Claims
The first independence claim is that `Date` is independent of `Latitude` after controlling for `DD`. So, I need to obtain the *precise* null probability for this claim. Choosing the correct modeling procedure requires identifying the appropriate distribution of the dependent variable, in this case `Date`. Using some helper functions and the `pairs()` function in the base `graphics` package I can look at the correlations and distributions simultaneously.

```{r helper functions for scatterplot matrix, echo=FALSE}
# These were copied from the help pages of the `pairs` function with minor alterations
